Score-based tests of measurement invariance: Use in practice

### 2013-09-25 frontiers/frontiers.Rnw
Minor updates to frontiers.Rnw: o Revised subscripts in path diagram o Removed single quotes in Sweave chunks due to issues with texlive
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@266 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<preliminaries1,echo=FALSE>>=
## packages
library("lavaan")
library("strucchange")
library("mvtnorm")
library("lattice")

@@

## remove cases with 'imputed' values(not in 1,...,9)
compcases <- apply(YouthGratitude[,4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases,]
@
Next, we fit two models in lavaan: a one-factor model where loadings are restricted 
to be equal across age groups, and a one-factor model where loadings are free across age groups.
<<modest>>=
## Restricted model
reduced <- cfa('f1=~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5',
             data=yg, group="agegroup", meanstructure=TRUE,
             group.equal="loadings")

## Unrestricted model
full <- cfa('f1=~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5',
             data=yg, group="agegroup", meanstructure=TRUE)
@
Finally, we can get the results of a likelihood ratio test via the \verb+anova()+ 
function, which implies that the GQ-6 violates measurement invariance.
<<LRT>>=
## LRT
anova(full, reduced)
@

@@

\node[error] (E1) at (7,6) {E1}
   edge [post] node[auto,swap]{\small{1}}(SCALE1)
   edge [errorsling, bend right=100]node[right=0.1,text width=2cm]{\scriptsize{$\psi_{11}=26.77$}} (E1.45);
\node[error] (E2) at (7,4.5) {E2}
   edge [post] node[auto,swap]{\small{1}} (SCALE2)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{22}=13.01$}}(E2.45);
\node[error] (E3) at (7,3) {E3}
   edge [post] node[auto,swap]{\small{1}}(SCALE3)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{33}=30.93$}}(E3.45);
\node[error] (E4) at (7,1) {E4}
   edge [post] node[auto,swap]{\small{1}}(SCALE4)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{44}=3.17$}}(E4.45);
\node[error] (E5) at (7,-0.5) {E5}
   edge [post] node[auto,swap]{\small{1}}(SCALE5)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{55}=8.82$}} (E5.45);
\node[error] (E6) at (7,-2) {E6}
   edge [post] node[auto,swap]{\small{1}}(SCALE6)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{11}=22.5$}}(E6.45);

>>>>

\include{Sweave}
<<preliminaries1,echo=FALSE>>=
## packages
library("lavaan")
library("strucchange")
library("mvtnorm")
library("lattice")

@@

## remove cases with imputed values(not in 1,...,9)
compcases <- apply(YouthGratitude[,4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases,]
@
Next, we fit two models in lavaan: a one-factor model where loadings are restricted 
to be equal across age groups, and a one-factor model where loadings are free across age groups.
<<modest>>=
## Restricted model
reduced <- cfa("f1=~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
             data=yg, group="agegroup", meanstructure=TRUE,
             group.equal="loadings")

## Unrestricted model
full <- cfa("f1=~gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
             data=yg, group="agegroup", meanstructure=TRUE)
@
Finally, we can get the results of a likelihood ratio test via the \verb+anova()+ 
function, which implies that the GQ-6 violates measurement invariance.
<<LRT>>=
## LRT
anova(full, reduced)
@

@@

\node[error] (E1) at (7,6) {E1}
   edge [post] node[auto,swap]{\small{1}}(SCALE1)
   edge [errorsling, bend right=100]node[right=0.1,text width=2cm]{\scriptsize{$\psi_{11}=26.77$}} (E1.45);
\node[error] (E2) at (7,4.5) {E2}
   edge [post] node[auto,swap]{\small{1}} (SCALE2)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{22}=13.01$}}(E2.45);
\node[error] (E3) at (7,3) {E3}
   edge [post] node[auto,swap]{\small{1}}(SCALE3)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{33}=30.93$}}(E3.45);
\node[error] (E4) at (7,1) {E4}
   edge [post] node[auto,swap]{\small{1}}(SCALE4)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{44}=3.17$}}(E4.45);
\node[error] (E5) at (7,-0.5) {E5}
   edge [post] node[auto,swap]{\small{1}}(SCALE5)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{55}=8.82$}} (E5.45);
\node[error] (E6) at (7,-2) {E6}
   edge [post] node[auto,swap]{\small{1}}(SCALE6)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]{\scriptsize{$\psi_{66}=22.5$}}(E6.45);
